Tools and Ideas for the Proceedural Generation of Shadow Sculptures.

### 2015-12-14 paper/paper.tex
something something did something

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[toc,page]{appendix}

@@

Each of Larry Kagan's sculptures consists of a metal structure
composed of bent rods of metal mounted to a wall and illuminated by
a bright light from a carefully chosen location. The eye is drawn to
the shadow produced this way, which forms a familiar image, while the
rods themselves often have no obvious pattern. In the simplest case,
the shadow image is a line drawing and the rods are attached to the
wall at several points. For example, the piece "Frankfurt Chair" is
like this. Kagan has created many variations on this idea including
incorporating some of the bent rods in the recognizable image while
most of the image is formed by the shadow, as seen in "Beach Chair".
"Intersection of Two Circles" shows that a sculpture composed of rods
can have a solid shadow with a geometric shape. The light source can
be on the ceiling cented over the piece or be off to one side as it
is in "At". With the light source on one side the shadow falls
predominantly on the side of the sculpture. Despite the fact that a
single small bright light source is installed to cast the shadow for
each sculpture, soft egdes of the shadow are noticeable in many of
these works. In "Mosquito I", Kagan uses this effect in a dramatic
way; the image present in the shadow of this sculpture is a mosquito
with its own shadow cast by an imaginary light source. In order to
make the distinction obvious, Kagan allowed soft shadow edges to show
in the portion of the image corresponding to the imaginary shadow of
the mosquito, but created the image of the mosquito with dark
hard-edged shadows.

@@

The first representation is used when saving a sculpure as a digital file. These files can be given as input to the visualization system that is described later in this paper. The informal specification of this format can be found in the file 'ad file spec.txt' in the git repository submitted with this paper. An example file in this format can be generated by the script make-art-description.py, which is also in the git repository.

The contents of such a file include three things that represent the sculpture: the position of the light source (actually a list of point sources, so we can simulate a diffuse source), the radius of the bar stock to use in constructing the sculpture and a list of 'strands'. Each strand is a list of points in 3D space, and it represents a space-filling shape composed of the union of spheres centered at each point and of cylinders with the centers of their end faces at consecutive points in the strand. The idea is that a strand approximates a smoothly bending piece of steel bar. One could construct the sculpture by making each strand from bar stock, then holding each strand in place and welding them together wherever they make contact.

@@

The first method is partially implemented in the file 'rayTracing.py' on the branch 'master' in the submitted git repository. In this method the cast shadow of each sphere and cylinder is computed individually and merged. Here is some pseudo-code for rendering the shadow of a collection of spheres and cylinders illuminated by a single point light source:

@@

It should also be very fast to render shadows using openGL. Shadowmaps are a standard technique for rendering dynamic shadows. In shadowmapping, a scene is rendered from the perspective of a point light source and the resulting "image" is colored according to how far each part of the image is from the light. Shadowmapping typically goes on to use this information to shade a rendering of the same scene from another perspective, but we only want an image of the shadow on the wall.

\section{Genetic Algorithm Solutions}
We believe approximate solutions to the forward problem may be possible using genetic algorithms for creating "abstract" data that fits a given shadow.  The question then becomes how to represent data for each possible solution to the problem in a genome that allows simple crossovers and mutations.  Some possible representations are as follows:

@@

\begin{appendices}
\chapter{A} \label{a}
In this appendix we will show in detail the calculation of the boundary of a shadow cast by a sphere by a point light source. The shadow is cast on the z=0 plane. On the z-axis the sphere is strictly between the light and the plane. We are given the location of the 
\end{appendices}

>>>>

\documentclass[letter,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[toc,page]{appendix}

@@

Each of Larry Kagan's sculptures consists of a metal structure
composed of bent rods of metal mounted to a wall and illuminated by
a bright light from a carefully chosen location. The eye is drawn to
the shadow produced this way, which forms a familiar image, while the
rods themselves often have no obvious pattern. In the simplest case,
the shadow image is a line drawing and the rods are attached to the
wall at several points. For example, the piece ``Frankfurt Chair'' is
like this. Kagan has created many variations on this idea including
incorporating some of the bent rods in the recognizable image while
most of the image is formed by the shadow, as seen in ``Beach Chair''.
``Intersection of Two Circles'' shows that a sculpture composed of rods
can have a solid shadow with a geometric shape. The light source can
be on the ceiling cented over the piece or be off to one side as it
is in ``At''. With the light source on one side the shadow falls
predominantly on the side of the sculpture. Despite the fact that a
single small bright light source is installed to cast the shadow for
each sculpture, soft egdes of the shadow are noticeable in many of
these works. In ``Mosquito I'', Kagan uses this effect in a dramatic
way; the image present in the shadow of this sculpture is a mosquito
with its own shadow cast by an imaginary light source. In order to
make the distinction obvious, Kagan allowed soft shadow edges to show
in the portion of the image corresponding to the imaginary shadow of
the mosquito, but created the image of the mosquito with dark
hard-edged shadows.

@@

The first representation is used when saving a sculpure as a digital file. These files can be given as input to the visualization system that is described later in this paper. The informal specification of this format can be found in the file `ad file spec.txt' in the git repository submitted with this paper. An example file in this format can be generated by the script make-art-description.py, which is also in the git repository.

The contents of such a file include three things that represent the sculpture: the position of the light source (actually a list of point sources, so we can simulate a diffuse source), the radius of the bar stock to use in constructing the sculpture and a list of `strands'. Each strand is a list of points in 3D space, and it represents a space-filling shape composed of the union of spheres centered at each point and of cylinders with the centers of their end faces at consecutive points in the strand. The idea is that a strand approximates a smoothly bending piece of steel bar. One could construct the sculpture by making each strand from bar stock, then holding each strand in place and welding them together wherever they make contact.

@@

The first method is partially implemented in the file `rayTracing.py' on the branch `master' in the submitted git repository. In this method the cast shadow of each sphere and cylinder is computed individually and merged. Here is some pseudo-code for rendering the shadow of a collection of spheres and cylinders illuminated by a single point light source:

@@

It should also be very fast to render shadows using openGL. Shadowmaps are a standard technique for rendering dynamic shadows. In shadowmapping, a scene is rendered from the perspective of a point light source and the resulting ``image'' is colored according to how far each part of the image is from the light. Shadowmapping typically goes on to use this information to shade a rendering of the same scene from another perspective, but we only want an image of the shadow on the wall.

\section{Genetic Algorithm Solutions}
We believe approximate solutions to the forward problem may be possible using genetic algorithms for creating ``abstract'' data that fits a given shadow.  The question then becomes how to represent data for each possible solution to the problem in a genome that allows simple crossovers and mutations.  Some possible representations are as follows:

@@

\begin{appendices}
\chapter{Appendix A} \label{a}

In this appendix we will show in detail the calculation of the boundary of a shadow cast by a sphere by a point light source. The shadow is cast on the z=0 plane. On the z-axis the sphere is strictly between the light and the plane. We are given $\vec{l}$, the location of the point light source, $\vec{c}$, the center of the sphere, and $r$, its radius.

The first step is to derive the equation of the shadow cone. A generic point on the cone will be denoted by $\vec{x}$. The axis of the cone passes through $\vec{l}$ and through $\vec{c}$. The defining property of a point $\vec{x}$ is

$\|proj_{\vec{p}-\vec{l}} \vec{x}\| = \|orth_{\vec{p}-\vec{l}} \vec{x}\|c$

where c is a constant characteristic of the aperture of the cone.

\end{appendices}
